TAPIR: Threaded Application Programming on Intermittent Resources

### 2017-05-11 paper.tex
italics

Commonly, an energy-harvesting devices charges and collects power in a storage capacitor until the capacitor reaches a sufficient level of charge.
Once the capacitor is charged, the device begins its operation phase and will run until the capacitor is drained.
This leads to the [intermittent execution model] where regular shut downs and reboots to recharge are the common case rather than the rare case in
a traditional execution model. Because the intermittent execution model includes power failures and reboots, continuous execution programs behave
irregular behavior on an intermittent device and a new programming model is needed.

>>>>

Commonly, an energy-harvesting devices charges and collects power in a storage capacitor until the capacitor reaches a sufficient level of charge.
Once the capacitor is charged, the device begins its operation phase and will run until the capacitor is drained.
This leads to the \textit{intermittent execution model} where regular shut downs and reboots to recharge are the common case rather than the rare case in
a traditional execution model. Because the intermittent execution model includes power failures and reboots, continuous execution programs behave
irregular behavior on an intermittent device and a new programming model is needed.
